TreeFelling_Draft

### 2021-07-23 R/TreeFelling_Draft.Rmd
treefelling

# Polygon orientation
DescTools::Rotate(x= SelectedTrees$Xutm[1], y = SelectedTrees$Yutm[1] + SelectedTrees$TrunkHeight[1] + SelectedTrees$CrownHeight[1]/2,
                  theta = pi/sample(0:180, size = 1))

ggplot() + # plot 2 polygones
  geom_sf(data = Trunk) +
  geom_sf(data = Crown) 
# Multipolygone = tous les arbres
```
```{r}
for (ind in c(1:nrow(SelectedTrees))) {
  pts[ind] = list(matrix(c(SelectedTrees$Xutm[ind]-(SelectedTrees$DBH[ind]/100)/2, SelectedTrees$Yutm[ind], 
                    SelectedTrees$Xutm[ind]-(SelectedTrees$DBH[ind]/100)/2, SelectedTrees$Yutm[ind] + SelectedTrees$TrunkHeight[ind], 
                    SelectedTrees$Xutm[ind]+(SelectedTrees$DBH[ind]/100)/2, SelectedTrees$Yutm[ind] + SelectedTrees$TrunkHeight[ind], 
                    SelectedTrees$Xutm[ind]+(SelectedTrees$DBH[ind]/100)/2, SelectedTrees$Yutm[ind],
                    SelectedTrees$Xutm[ind]-(SelectedTrees$DBH[ind]/100)/2, SelectedTrees$Yutm[ind]) # retour
                  ,ncol=2, byrow=TRUE)) # DBH en cm à passer en m

@@

# le houppier
dat[ind] = data.frame(
  x = SelectedTrees$Xutm[ind], #centroid locations (x) m^me x que l'arbre
  y = SelectedTrees$Yutm[ind] + SelectedTrees$TrunkHeight[ind] + SelectedTrees$CrownHeight[ind]/2, #centroid locations (y) = hauteur du tronc + CrownHeight/2
  ex = SelectedTrees$CrownDiameter[ind]/2, #Size along x-axis (CrownDiameter/2)
  ey = SelectedTrees$CrownHeight[ind]/2, #Size along y-axis (CrownHeight/2)
  stringsAsFactors = FALSE
)
dat[ind] = st_as_sf(dat[ind], coords = c("x", "y")) #centroids

# Calculate ellipses
Crown[ind] = st_ellipse(pnt = dat[ind], ex = dat[ind]$ex, ey = dat$ey) # ne fctne pas
a[ind] <- st_difference(st_union(Crown[ind], Trunk[ind])) # -> multypolygon dont on garde que les points qui ne se superposent pas

@@

  Shadows <- st_multipolygon()
} 
# créer un polygone par arbre ("Shadow"):
# origine = coordonnées de l’arbre (vecteurs "AccessibleTreesPoints")
# sommet = 1 point au hasard
# longueur = hauteur de l’arbre TreeHeight
# largeur = DBH
# hauteur de l’ellipse CrownHeight
# diamètre de l’ellipse CrownDiameter

>>>>

a <- st_difference(st_union(Crown, Trunk)) # -> multypolygon dont on garde que les points qui ne se superposent pas
# a <- st_cast(a, "POLYGON")
plot(a)

ggplot() + # plot 2 polygones
  geom_sf(data = Trunk) +
  geom_sf(data = Crown) 
# Multipolygone = tous les arbres
```

# Treefelling orientation
(voir shéma sur google slides)
1) choper le point (Trail) de la pistele plus proche de l'emplacement de l'arbre (Foot)
2) calculer l'angle (theta) entre le vecteur que forme la hauteur de l'arbre et le vecteur opposé à celui formé entre le point "Foot" et le point "Trail", par rapport au point "Foot"
3) rotation du polygone d'un angle de 60 +/- theta °

```{r}
# Create a polygon ScndTrail
pts = list(matrix(c(286520, 583134,
                    286520, 583240, 
                    286524, 583240, 
                    286524, 583134,
                    286520, 583134) # retour
                  ,ncol=2, byrow=TRUE)) # DBH en cm à passer en m

(ScndTrail = st_polygon(pts))
ggplot() + # plot 2 polygones
  geom_sf(data = a) +
  geom_sf(data = ScndTrail)

# Find the point (Trail) on the ScndTrail closest to the location of the tree (Foot)
Foot <- st_point(c(SelectedTrees$Xutm[1],SelectedTrees$Yutm[1]))

NearestPoints <- st_nearest_points(Foot, ScndTrail) # from the Foot of the tree to the ScndTrail

NearestPoint <- st_cast(NearestPoints, "POINT") # to have start (Foot) and end (Trail) points
Trail <- NearestPoint[[2]] # the point (Trail) on the ScndTrail closest to the location of the tree (Foot)

ggplot() + # plot 2 polygones
  geom_sf(data = a) + # the tree (polygone)
  geom_sf(data = Foot) + # the foot of the tree (point)
  geom_sf(data = ScndTrail) + # the 2nd trail (polygone)
  geom_sf(data = NearestPoints) + # the shortest way from the foot to the trail
  geom_sf(data = Trail) # the point on the ScndTrail closest to the location of the tree (Foot)

Trail[1]

# Compute theta angle
theta <- as.numeric(matlib::angle(c(Foot[1] - Foot[1], Foot[2] + SelectedTrees$TreeHeight[1]),
                                  c(Foot[1] - Trail[1], Foot[2] -Trail[2]), degree = TRUE))

```
# Tree rotation
ref : https://github.com/jeffreyevans/spatialEco/blob/master/R/rotate.polygon.R
```{r}

RotatePolygon <- function(p, angle, fixed) { # angle in the clockwise direction

  p.coords <- sf::st_coordinates(p)[,1:2] # Polygone coordinates extraction

  p.center <- suppressWarnings(sf::st_coordinates(fixed))

  rotate.coords <- function(xy, a, center) {

    co <- cos(-a * pi / 180)

    si <- sin(-a * pi / 180)

    adj <- matrix(rep(center, nrow(xy)), ncol=2, byrow=TRUE) # matrix with fixed point coordinates

    xy <- xy-adj

    cbind(co * xy[,1] - si * xy[,2],si * xy[,1] + co * xy[,2]) + adj
  }

  p.rotate <- rotate.coords(p.coords, a = angle, center = c(p.center[1], 
                                                            p.center[2]))

  Turned <- sf::st_sfc(sf::st_polygon(list(p.rotate))) # create the turned polygon

  return(Turned)

TurnedTrunkA <- RotatePolygon(Trunk, angle = 60 - theta, fixed = Foot) # turned trunk
TurnedCrownA <- RotatePolygon(Crown, angle = 60 - theta, fixed = Foot) # turned crown
TurnedTrunkB <- RotatePolygon(Trunk, angle = 300 - theta, fixed = Foot) # turned trunk (angle in the clockwise direction: 360-60-theta)
TurnedCrownB <- RotatePolygon(Crown, angle = 300 - theta, fixed = Foot) # turned crown (angle in the clockwise direction)

# For a random direction felling
RandomAngle <- sample(c(0:180), size = 1)
RandomTrunk <- RotatePolygon(Trunk, angle = RandomAngle, fixed = Foot) # turned trunk
RandomCrown <- RotatePolygon(Crown, angle = RandomAngle, fixed = Foot) # turned crown

ggplot() + # plot 2 polygones
  geom_sf(data = a) + # the tree (polygone)
  geom_sf(data = Foot) + # the foot of the tree (point)
  geom_sf(data = ScndTrail) + # the 2nd trail (polygone)
  geom_sf(data = NearestPoints) + # the shortest way from the foot to the trail
  geom_sf(data = Trail) + # the point on the ScndTrail closest to the location of the tree (Foot)
  geom_sf(data = TurnedTrunkA) +
  geom_sf(data = TurnedCrownA) +
  geom_sf(data = TurnedTrunkB) +
  geom_sf(data = TurnedCrownB) +
  geom_sf(data = RandomTrunk) +
  geom_sf(data = RandomCrown)

# Create the line to pull the tree
```{r}
p = NearestPoints
angle = 60
fixed = "foot"

RotateLine <- function(p, angle = 60,  
    fixed = c("foot", "center", "lower.left", "upper.right")) {
# if(class(p)[1] != "sf") p <- sf::st_as_sf(p)
p.coords <- sf::st_coordinates(p)[,1:2] # Polygone coordinates extraction

if(fixed[1] == "foot") {
p.center <- suppressWarnings(sf::st_coordinates(Foot))

} else if (fixed[1] == "center") {
  p.center <- suppressWarnings(sf::st_coordinates(sf::st_centroid(p)))

} else if(fixed[1] == "lower.left") {

  p.center <- c(min(sf::st_coordinates(p)[,1]),
                min(sf::st_coordinates(p)[,2]))

} else if(fixed[1] == "upper.right") {
  p.center <- c(max(sf::st_coordinates(p)[,1]),
                max(sf::st_coordinates(p)[,2]))
}

rotate.coords <- function(xy, a, center) {

  co <- cos(-a * pi / 180)

  si <- sin(-a * pi / 180)

  adj <- matrix(rep(center, nrow(xy)), ncol=2, byrow=TRUE) # matrix with fixed point coordinates

  xy <- xy-adj

  cbind(co * xy[,1] - si * xy[,2],si * xy[,1] + co * xy[,2]) + adj
}

p.rotate <- rotate.coords(p.coords, a = angle, center = c(p.center[1], 
                                                          p.center[2]))

Turned <- sf::st_sfc(sf::st_linestring(p.rotate)) # create the new polygon

return(Turned)

Trace <- RotateLine(NearestPoints, angle = 60, fixed = "foot")

ggplot() + # plot 2 polygones
  geom_sf(data = a) + # the tree (polygone)
  geom_sf(data = Foot) + # the foot of the tree (point)
  geom_sf(data = ScndTrail) + # the 2nd trail (polygone)
  geom_sf(data = NearestPoints) + # the shortest way from the foot to the trail
  geom_sf(data = Trail) + # the point on the ScndTrail closest to the location of the tree (Foot)
  geom_sf(data = TurnedTrunk) +
  geom_sf(data = TurnedCrown) +
  geom_sf(data = Trace)

# All the selected trees

```{r}
for (ind in c(1:nrow(SelectedTrees))) {
  pts[ind] = list(matrix(c(SelectedTrees$Xutm[ind]-(SelectedTrees$DBH[ind]/100)/2, SelectedTrees$Yutm[ind], 
                           SelectedTrees$Xutm[ind]-(SelectedTrees$DBH[ind]/100)/2, SelectedTrees$Yutm[ind] + SelectedTrees$TrunkHeight[ind], 
                           SelectedTrees$Xutm[ind]+(SelectedTrees$DBH[ind]/100)/2, SelectedTrees$Yutm[ind] + SelectedTrees$TrunkHeight[ind], 
                           SelectedTrees$Xutm[ind]+(SelectedTrees$DBH[ind]/100)/2, SelectedTrees$Yutm[ind],
                           SelectedTrees$Xutm[ind]-(SelectedTrees$DBH[ind]/100)/2, SelectedTrees$Yutm[ind]) # retour
                         ,ncol=2, byrow=TRUE)) # DBH en cm à passer en m

@@

  # le houppier
  dat[ind] = data.frame(
    x = SelectedTrees$Xutm[ind], #centroid locations (x) m^me x que l'arbre
    y = SelectedTrees$Yutm[ind] + SelectedTrees$TrunkHeight[ind] + SelectedTrees$CrownHeight[ind]/2, #centroid locations (y) = hauteur du tronc + CrownHeight/2
    ex = SelectedTrees$CrownDiameter[ind]/2, #Size along x-axis (CrownDiameter/2)
    ey = SelectedTrees$CrownHeight[ind]/2, #Size along y-axis (CrownHeight/2)
    stringsAsFactors = FALSE
  )
  # dat[ind] = st_as_sf(dat[ind], coords = c("x", "y")) #centroids

  # Calculate ellipses
  # Crown[ind] = st_ellipse(pnt = dat[ind], ex = dat[ind]$ex, ey = dat$ey) # ne fctne pas
  # a[ind] <- st_difference(st_union(Crown[ind], Trunk[ind])) # -> multypolygon dont on garde que les points qui ne se superposent pas

@@

  Shadows <- st_multipolygon()
} 
# créer un polygone par arbre ("Shadow"):
# origine = coordonnées de l’arbre (vecteurs "AccessibleTreesPoints")
# orientation = angle au hasard
# longueur = hauteur de l’arbre TreeHeight
# largeur = DBH
# hauteur de l’ellipse CrownHeight
# diamètre de l’ellipse CrownDiameter
